Supplementary information

### 2021-09-27 _targets.Rmd
add toy example sketch

---
title: "Supplementary information"
output: html_document
---

@@

An exponential process with a certain rate r; and 3 forecasting models: one that thinks it’s exponential with rate r-a , one that thinks it’s exponential with rate r+a and one that thinks it’s linear; and compare scoring on linear and log scale for increasing horizons.

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = c(0, 0.01, 0.1, -0.01, -0.1),
  r_error = c(0, 0.01, 0.05, 0.1, -0.01, -0.05, -0.1),
  additive_error = c(0, 1, 10, -1, -10)
) |> 
  mutate(id = 1:n())
```

```{targets toy_simulations, tar_simple = TRUE}
toy_scenarios |>
  rowwise() |>
  mutate(y = list(
    simulate_exp_poisson(init = init, time = 10, growth = r + r_error,
                         additive_error = additive_error, sims = 1000)
    )
  ) |>
  unnest(cols = c(y))
```

@@

@@

```{targets, toy_scores, tar_simple = TRUE}
toy_forecasts |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error"),
    metrics = c("crps")
  )
```

```{targets, toy_log_scores, tar_simple = TRUE}
toy_forecasts |>
  mutate(across(.cols = c("true_value", "prediction"), ~ log(.x))) |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error"),
    metrics = c("crps")
  )
```

>>>>

---
title: "Supplementary information"
output: github_document
---

@@

As a toy example we simulate a grid of data with varying exponential growth rates and a Poisson observation model. As example forecasts we use the same simulation model but add error to either the growth rate or the mean of observations. We do this using the following steps,

- Define a grid of scenarios including the true values (zero growth rate or cumulative linear error).

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = c(0, 0.01, 0.1, -0.01, -0.1),
  r_error = c(0, 0.01, 0.025, 0.05, 0.1, -0.01, -0.025, -0.05, -0.1),
  additive_error = c(0, 1, 10, -1, -10)
) |> 
  mutate(id = 1:n())
```

- Simulate each scenario a 1000 times.

```{targets toy_simulations, tar_simple = TRUE}
toy_scenarios |>
  rowwise() |>
  mutate(y = list(
    simulate_exp_poisson(init = init, time = 4, growth = r + r_error,
                         additive_error = additive_error, sims = 1000)
    )
  ) |>
  unnest(cols = c(y))
```

- Filter for the "truth" scenario and keep only the first simulation.

@@

- Filter for all other scenarios.

@@

- Score example forecasts and summarise by growth rate, growth rate error, additive error, and forecast horizon.

```{targets, toy_scores, tar_simple = TRUE}
toy_forecasts |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error", "time"),
    metrics = c("crps")
  )
```

- Repeat the scoring process but on the log scale.

```{targets, toy_log_scores, tar_simple = TRUE}
toy_forecasts |>
  mutate(across(.cols = c("true_value", "prediction"), ~ log(.x))) |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error", "time"),
    metrics = c("crps")
  )
```

- Join log and natural scale scores.

```{targets, toy_all_scores, tar_simple = TRUE}
toy_log_scores |>
  mutate(scale = "log") |>
  bind_rows(
    toy_scores |>
      mutate(scale = "natural")
  )
```

- Plot natural scale scores by horizon.

```{targets plot_toy_scores_by_horizon, tar_simple = TRUE}
toy_scores |>
  filter(time <= 4) |>
  plot_scores_by_horizon()
```

- Plot log scale scores by horizon.

```{targets plot_toy_log_scores_by_horizon, tar_simple = TRUE}
toy_log_scores |>
  filter(time <= 4) |>
  plot_scores_by_horizon()
```

- Plot log and natural scale scores for the 4 week horizon.

```{targets plot_toy_scores_by_scale, tar_simple = TRUE}
toy_all_scores |>
  filter(time == 4) |>
  plot_scores_by_scale()
```

- Save output for external use.

```{targets save_toy_output}
list(
  tar_target(
    toy_scores_csv, 
    save_csv(toy_all_scores, here("output/data/toy_all_scores.csv")),
    format = "file"
  ),
  tar_target(
    toy_scores_by_scale_file, 
    save_plot(plot_toy_scores_by_scale, 
              here("output", "figures", "toy_scores_by_scale.png"),
    format = "file")
            ),
  tar_target(
    toy_scores_by_horizon_file, 
    save_plot(plot_toy_scores_by_horizon, 
              here("output", "figures", "toy_scores_by_horizon.png"),
    format = "file")
            ),
  tar_target(
    toy_log_scores_by_horizon_file, 
    save_plot(plot_toy_log_scores_by_horizon, 
              here("output", "figures", "toy_log_scores_by_horizon.png"),
    format = "file")
            )
)
```
